The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-05-22 ms/ms.tex
overleaf

One such fundamental model development step is parameter sensitivity testing and/or parameter optimization \cite{qian2018}.
Because parameter values are uncertain, evaluating the effect of parameter values on model output is critical to the model development process \cite{hourdin2017,balaji2022}.
When applied systematically, the result is a Parameter Perturbation Ensemble (PPE), alternatively termed a Perturbed Physics Ensemble.
PPEs have played an important role in assessing projection uncertainty in climate models \cite{murphy2004,sanderson2008,booth2012,hawkins2019,yamazaki2021,peatier2022,tett2022}.
PPEs also form a basis for automated model calibration through, for example, history matching \cite{williamson2013} (Williamson2017; GMD-NEMO calibration; Couvreux2020 JAMES; Hourdin 2020 JAMES) or Bayesian uncertainty quantification \cite{cleary2021}.
Our goal in this project is to systematize parameter perturbation activity within our modeling framework, and develop the necessary tools and datasets to efficiently test parameter effects across the full suite of land model processes. 
In doing so, we have generated a large PPE, comprising thousands of parameter sensitivity tests.
In this paper we present that dataset, describe how it was produced, and survey some potential applications.

>>>>

One such fundamental model development step is parameter sensitivity testing and/or parameter optimization \cite{qian2018}.
Because parameter values are uncertain, evaluating the effect of parameter values on model output is critical to the model development process \cite{hourdin2017,balaji2022}.
When applied systematically, the result is a Parameter Perturbation Ensemble (PPE), alternatively termed a Perturbed Physics Ensemble.
PPEs have played an important role in assessing projection uncertainty in climate models \cite{murphy_2004,sanderson2008,booth2012,hawkins2019,yamazaki2021,peatier2022,tett2022}.
PPEs also form a basis for automated model calibration through, for example, history matching \cite{williamson2013,williamson2017,hourdin2020,couvreux2021} or Bayesian uncertainty quantification \cite{cleary2021}.
Our goal in this project is to systematize parameter perturbation activity within our modeling framework, and develop the necessary tools and datasets to efficiently test parameter effects across the full suite of land model processes. 
In doing so, we have generated a large PPE, comprising thousands of parameter sensitivity tests.
In this paper we present that dataset, describe how it was produced, and survey some potential applications.
